Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-16 R0V0.tex
Modify the paragraph about ADMM

\mypara Condition~\eqref{eq:Arstein-Sontag} is satisfied, whenever the matrix inequality
\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
 	\ker(B)^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)\ker(B)\prec0
\end{equation} 
holds, where $\ker(B)$ is a full-rank matrix satisfying $B^\top\ker(B)\equiv0$.

@@

\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.

>>>>

\mypara Condition~\eqref{eq:Arstein-Sontag} is satisfied, whenever the matrix inequality
\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
 	B_\perp^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)B_\perp\prec0
\end{equation} 
holds, where $B_\perp$ is a full-rank matrix satisfying $B B_\perp\equiv0$.

@@

\mypara In the remainder of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara Note that the ADMM cannot be used to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual}. The reason is the fact that $B_\perp\equiv0$.
